ODGI: scalable tools for working with pangenome graphs

### 2021-05-29 manuscript/main.tex
reduced the comments

%    Text Text Text Text Text Text Text Text Text Text Text Text Text
%    Text Text Text Text Text Text Text Text. Figure~\ref{fig:01}
%    shows that the above method Text Text Text Text Text Text Text
%    Text Text Text Text Text.  \citep{Bag01} wants to know about
%        {\ldots}{\ldots} text follows.
%    \begin{equation}
%        \sum \text{\it x}+ \text{\it y} =\text{\it Z}\label{eq:01}\vspace*{-10pt}
%    \end{equation}

@@

%    \section{Approach}
%
%    Equation~(\ref{eq:01}) Text Text Text Text Text Text Text Text
%    Text Text Text Text Text Text Text Text Text Text Text Text Text.
%    Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%    Text Text Text Text Text Text Text Text Text Text Text.
%    \citealp{Boffelli03} might want to know about text text text text
%    .....

@@

        ODGI is designed to build and modify paths in parallel, keeping its representation in memory efficient. It
        applies concepts first introduced in the dynamic version of the Graph BWT citep{31406990}, a scalable
        implementation of the graph extension of the positional Burrows-Wheeler transform \citep{28702075}. Specifically,
        we build a \textit{node-local} model of the graph, where the graph is stored in a vector of node structures.
        The identifier of each node is its offset in this vector plus 1. Each structure contains the sequence of the
        node, its edges in both directions (forward and backward), and a vector of \textit{path steps} that describes
        how the embedded paths walk across the node. Each step records the path identifier and the previous and next
        path steps on the same path. To reduce the encoding, we encode path steps using a local alphabet that maps the
        \textit{N} neighbors of the node into the range \textit{1..N}. To further save space, \textit{node deltas},
        rather than IDs, are stored in this alphabet. The delta between two nodes is defined as their distance in the
        graph vector (i.e., the difference between the node offsets). The path step vector, of length \textit{n}, is
        stored using a dynamic succinct integer vector that requires \textit{O(5nw)} bits, where \textit{w} is
        \textit{\textasciitilde log\textsubscript{2}(N)}. Finally, to allow operating on path steps in parallel, each node structure includes a
        byte-width mutex lock.

%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text
%        text\vspace*{1pt}

%        \begin{itemize}
%            \item for bulleted list, use itemize
%            \item for bulleted list, use itemize
%            \item for bulleted list, use itemize\vspace*{1pt}
%        \end{itemize}

%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text\vadjust{\newpage}.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%
%
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%
%
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%
%        \subsection{This is subheading}
%
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text
%        text. Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%
%        \subsubsection{This is subsubheading}
%
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%
%
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text\break
%        text text
%
%
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text
%        textText Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%
%        \enlargethispage{6pt}
%
%
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%
%
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%
%
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%
%
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%
%        \begin{table}[!t]
%            \processtable{This is table caption\label{Tab:01}} {\begin{tabular}{@{}llll@{}}
%                                                                    \toprule head1 &
%                                                                    head2 & head3 & head4 \\\midrule
%                                                                    row1 & row1 & row1 & row1 \\
%                                                                    row2 & row2 & row2 & row2 \\
%                                                                    row3 & row3 & row3 & row3 \\
%                                                                    row4 & row4 & row4 & row4 \\\botrule
%            \end{tabular}}{This is a footnote}
%        \end{table}

@@

%    Text Text Text Text Text Text Text Text Text Text Text Text Text
%    Text Text Text Text Text Text Text Text.
%    Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%    Text Text Text Text Text Text Text Text Text Text Text.
%    \citealp{Boffelli03} might want to know about text text text text
%    Text Text Text Text Text Text Text Text Text Text Text Text Text
%    Text Text Text Text Text Text Text Text.
%    Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%    Text Text Text Text Text Text Text Text Text Text Text.
%    \citealp{Boffelli03} might want to know about text text text text
%    Text Text Text Text Text Text Text Text Text Text Text Text Text
%    Text Text Text Text Text Text Text Text.
%    Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%    Text Text Text Text Text Text Text Text Text Text Text.
%    \citealp{Boffelli03} might want to know about text text text text
%
%    \subsection{Test1}
%
%    Text Text Text Text Text Text Text Text Text Text Text Text Text
%    Text Text Text Text Text Text Text Text.
%    Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%    Text Text Text Text Text Text Text Text Text Text Text.
%    \citealp{Boffelli03} might want to know about text text text text
%    Text Text Text Text Text Text Text Text Text Text Text Text Text
%    Text Text Text Text Text Text Text Text.
%    Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%    Text Text Text Text Text Text Text Text Text Text Text.
%    \citealp{Boffelli03} might want to know about text text text text
%    Text Text Text Text Text Text Text Text Text Text Text Text Text
%    Text Text Text Text Text Text Text Text.
%    Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%    Text Text Text Text Text Text Text Text Text Text Text.
%    \citealp{Boffelli03} might want to know about text text text text
%
%
%    \section{Discussion}
%
%    Text Text Text Text Text Text Text Text Text Text Text Text Text
%    Text Text Text Text Text Text Text Text.
%    Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%    Text Text Text Text Text Text Text Text Text Text Text.
%    \citealp{Boffelli03} might want to know about text text text text
%    Text Text Text Text Text Text Text Text Text Text Text Text Text
%    Text Text Text Text Text Text Text Text.
%    Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%    Text Text Text Text Text Text Text Text Text Text Text.
%    \citealp{Boffelli03} might want to know about text text text text
%    Text Text Text Text Text Text Text Text Text Text.
%
%
%    Table~\ref{tab:01} shows that Text Text Text Text Text Text Text
%    Text Text Text Text. Figure~2\vphantom{\ref{fig:02}} shows that
%    the above method Text Text. Text Text Text Text Text Text Text
%    Text Text. Figure~2\vphantom{\ref{fig:02}} shows that the above
%    method Text Text. Text Text Text Text Text Text Text Text Text.
%    Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%    Text.

@@

%    \section{Conclusion}
%
%    (Table~\ref{tab:01}) Text Text Text Text Text Text Text Text Text
%    Text Text Text Text Text Text Text Text Text Text Text Text.
%    Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%    Text Text Text Text Text Text Text Text Text Text Text.
%    \citealp{Boffelli03} might want to know about text text text text
%    Text Text Text Text Text Text Text Text Text Text Text Text Text
%    Text Text Text Text Text Text Text Text.
%    Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%    Text Text Text Text Text Text Text Text Text Text Text.
%    \citealp{Boffelli03} might want to know about text text text text
%    Text Text Text Text Text Text Text Text Text Text Text Text Text
%    Text Text Text Text Text Text Text Text.
%    Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%    Text Text Text Text Text Text Text Text Text Text Text.
%
%
%    Text Text Text Text Text Text Text Text Text Text Text Text Text
%    Text Text Text Text Text Text Text Text.
%    Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%    Text Text Text Text Text Text Text Text Text Text Text.
%    \citealp{Boffelli03} might want to know about text text text text
%
%    \begin{enumerate}
%        \item this is item, use enumerate
%        \item this is item, use enumerate
%        \item this is item, use enumerate
%    \end{enumerate}
%
%    Text Text Text Text Text Text Text Text Text Text Text Text Text
%    Text Text Text Text Text Text Text Text.
%    Figure~2\vphantom{\ref{fig:02}} shows\vadjust{\pagebreak} that the
%    above method Text Text Text Text Text Text Text Text Text Text
%    Text Text.  \citealp{Boffelli03} might want to know about text
%    text text text Text Text Text Text Text Text Text Text Text Text
%    Text Text Text Text Text Text Text Text Text Text Text.
%    Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%    Text Text Text Text Text Text Text Text Text Text Text.
%    \citealp{Boffelli03} might want to know about text text text text
%    Text Text Text Text Text Text Text Text Text Text Text Text Text
%    Text Text Text Text Text Text Text\break Text.
%
%
%    Text Text Text Text Text Text Text Text Text Text Text Text Text
%    Text Text Text Text Text Text Text Text.
%    Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%    Text Text Text\vspace*{-10pt}

>>>>

@@

@@

        ODGI is designed to build and modify paths in parallel, keeping its representation in memory efficient. It
        applies concepts first introduced in the dynamic version of the Graph BWT \citep{31406990}, a scalable
        implementation of the graph extension of the positional Burrows-Wheeler transform \citep{28702075}. Specifically,
        we build a \textit{node-local} model of the graph, where the graph is stored in a vector of node structures.
        The identifier of each node is its offset in this vector plus 1. Each structure contains the sequence of the
        node, its edges in both directions (forward and backward), and a vector of \textit{path steps} that describes
        how the embedded paths walk across the node. Each step records the path identifier and the previous and next
        path steps on the same path. To reduce the encoding, we encode path steps using a local alphabet that maps the
        \textit{N} neighbors of the node into the range \textit{1..N}. To further save space, \textit{node deltas},
        rather than IDs, are stored in this alphabet. The delta between two nodes is defined as their distance in the
        graph vector (i.e., the difference between the node offsets). The path step vector, of length \textit{n}, is
        stored using a dynamic succinct integer vector that requires \textit{O(5nw)} bits, where \textit{w} is
        \textit{\textasciitilde log\textsubscript{2}(N)}. Finally, to allow operating on path steps in parallel, each node structure includes a
        byte-width mutex lock.

%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text. Figure~\ref{fig:01}
%        shows that the above method Text Text Text Text Text Text Text
%        Text Text Text Text Text.  \citep{Bag01} wants to know about
%            {\ldots}{\ldots} text follows.
%        \begin{equation}
%            \sum \text{\it x}+ \text{\it y} =\text{\it Z}\label{eq:01}\vspace*{-10pt}
%        \end{equation}
%
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text
%        text\vspace*{1pt}
%
%        \begin{itemize}
%            \item for bulleted list, use itemize
%            \item for bulleted list, use itemize
%            \item for bulleted list, use itemize\vspace*{1pt}
%        \end{itemize}
%
%        \begin{enumerate}
%            \item this is item, use enumerate
%            \item this is item, use enumerate
%            \item this is item, use enumerate
%        \end{enumerate}
%
%        \subsection{This is subheading}
%
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%        Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
%        Text Text Text Text Text Text Text Text Text Text Text.
%        \citealp{Boffelli03} might want to know about text text text text
%        Text Text Text Text Text Text Text Text Text Text Text Text Text
%        Text Text Text Text Text Text Text Text.
%
%
%        \enlargethispage{6pt}
%
%        \begin{table}[!t]
%            \processtable{This is table caption\label{Tab:01}} {\begin{tabular}{@{}llll@{}}
%                                                                    \toprule head1 &
%                                                                    head2 & head3 & head4 \\\midrule
%                                                                    row1 & row1 & row1 & row1 \\
%                                                                    row2 & row2 & row2 & row2 \\
%                                                                    row3 & row3 & row3 & row3 \\
%                                                                    row4 & row4 & row4 & row4 \\\botrule
%            \end{tabular}}{This is a footnote}
%        \end{table}

@@

@@
